HTW Hybrid Models

### 2024-02-29 Model/hybrid.qmd
add older hybrid fits from l1l8 that I missed

folder_names <- c("e1_hybrid_n_iter_250_ntry_200_0637",
"e1_hybrid_n_iter_60_ntry_150_2335",
"e1_hybrid_n_iter_200_ntry_300_0741",
"e1_hybrid_n_iter_150_ntry_150_4749")

@@

lowest_error_model <- best_id %>%
  group_by(id, condit,Fit_Method) %>%
  summarise(Best_Model = Model[which.min(mean_error)],
            Lowest_error = min(mean_error),
            differential = min(mean_error) - max(mean_error)) %>%
  ungroup()

@@

folder_names <- c("e2_hybrid_n_iter_60_ntry_150_3658","e2_hybrid_n_iter_250_ntry_200_0540","e2_hybrid_n_iter_150_ntry_150_2904")

@@

folder_names <- c("e3_hybrid_n_iter_150_ntry_150_1757","e3_hybrid_n_iter_250_ntry_200_4300","e3_hybrid_n_iter_60_ntry_150_0946")

>>>>

folder_names <- c("e1_hybrid_n_iter_250_ntry_200_0637",
"e1_hybrid_n_iter_60_ntry_150_2335",
"e1_hybrid_n_iter_200_ntry_300_0741",
"e1_hybrid_n_iter_150_ntry_150_4749","e1_hybrid_n_iter_100_ntry_100_1435")

@@

@@

folder_names <- c("e2_hybrid_n_iter_60_ntry_150_3658","e2_hybrid_n_iter_250_ntry_200_0540","e2_hybrid_n_iter_150_ntry_150_2904","e2_hybrid_n_iter_100_ntry_100_3211")

@@

## E3
```{r}

folder_names <- c("e3_hybrid_n_iter_150_ntry_150_1757","e3_hybrid_n_iter_250_ntry_200_4300","e3_hybrid_n_iter_60_ntry_150_0946","e3_hybrid_n_iter_100_ntry_100_0545")
